\documentclass[11pt,twoside]{book}

%%Page Size (rev. 08/19/2016)
%\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={6in,9in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
\usepackage[inner=0.5in, outer=0.5in, top=0.5in, bottom=0.5in, papersize={5.5in,8.5in}, head=12pt, headheight=30pt, headsep=5pt]{geometry}
%% width of textblock = 324 pt / 4.5in
%% A5 = 5.8 x 8.3 inches -- if papersize is A5, then margins should be [inner=0.75in, outer=0.55in, top=0.4in, bottom=0.4in]


%%Header (rev. 4/11/2011)
\usepackage{fancyhdr}
 \pagestyle{fancy}
\renewcommand{\chaptermark}[1]{\markboth{#1}{}}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
 \fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{Vesperale O.P.}
\fancyhead[CO]{\leftmark}
 \fancypagestyle{plain}{ %
\fancyhf{} % remove everything
\renewcommand{\headrulewidth}{0pt} % remove lines as well
\renewcommand{\footrulewidth}{0pt}}



\usepackage[autocompile,allowdeprecated=false]{gregoriotex}
\usepackage{gregoriosyms}
\gresetgregoriofont[op]{greciliae}




%%Titles (rev. 9/4/2011) -- TOCLESS --- lets you have sections that don't appear in the table of contents

\setcounter{secnumdepth}{-1}

\usepackage[compact,nobottomtitles*]{titlesec}
\titlespacing*{\chapter}{0pt}{*0}{*1}
\titlespacing*{\section}{0pt}{*0}{*1}
\titlespacing*{\subsection}{0pt}{*0}{*1}
\titlespacing*{\subsubsection}{0pt}{*0}{*1}
\titleformat{\chapter} {\normalfont\LARGE\sc\center}{\thechapter}{1em}{}
\titleformat{\section} {\normalfont\Large\sc\center}{\thesection}{1em}{}
\titleformat{\subsection} {\normalfont\large\sc\center}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\normalfont\normalsize\sc\center}{\thesubsubsection}{1em}{}

\newcommand{\nocontentsline}[3]{}
\newcommand{\tocless}[2]{\bgroup\let\addcontentsline=\nocontentsline#1{#2}\egroup} %% lets you have sections that don't appear in the table of contents


%%%

%%Index (rev. December 11, 2013)
\usepackage[noautomatic,nonewpage]{imakeidx}


\makeindex[name=incipit,title=Index]
\indexsetup{level=\section,toclevel=section,noclearpage}

\usepackage[indentunit=8pt,rule=.5pt,columns=2]{idxlayout}


%%Table of Contents (rev. May 16, 2011)

%\usepackage{multicol}
%\usepackage{ifthen}
%\usepackage[toc]{multitoc}

%% General settings (rev. January 19, 2015)

\usepackage{ulem}

\usepackage[latin,english]{babel}
\usepackage{lettrine}

\usepackage{paracol}

\usepackage{fontspec}

\setmainfont[Ligatures=TeX,BoldFont=MinionPro-Bold,ItalicFont=MinionPro-It, BoldItalicFont=MinionPro-BoldIt]{MinionPro-Regular-Modified.otf}



%% Style for translation line
\grechangestyle{translation}{\fontsize{10}{10}\it\selectfont}
\grechangestyle{annotation}{\fontsize{10}{10}\selectfont}
\grechangestyle{commentary}{\textnormal\selectfont}
\gresetcustosalteration{invisible}

%\grechangedim{annotationseparation}{0.1cm}{scalable}

%\GreLoadSpaceConf{smith-four}

\frenchspacing

\usepackage{indentfirst} %%%indents first line after a section

\usepackage{graphicx}
%\usepackage{tocloft}

%%Hyperref (rev. August 20, 2011)
%\usepackage[colorlinks=false,hyperindex=true,bookmarks=true]{hyperref}
\usepackage{hyperref}
\hypersetup{pdftitle={Vesperale O.P. 2016}}
\hypersetup{pdfauthor={Order of Preachers}}
\hypersetup{pdfsubject={Liturgy}}
\hypersetup{pdfkeywords={Dominican, Liturgy, Order of Preachers, Dominican Rite, Liturgia Horarum, Divine Office}}

\newlength{\drop}



\begin{document}


%%%Initial Matter within Body (20 May 2011)
\raggedbottom

%%Combination
\chapter{Sunday Vespers}
\section{25\textsuperscript{th} Sunday of Ordinary Time}
\subsection{September 18, 2016}

\newpage

    \index[Varia]{Deus in adiutorium} \label{Deus in adiutorium (Varia)} \grecommentary[0pt]{} \gresetinitiallines{1} \grechangedim{maxbaroffsettextleft}{0 cm}{scalable} \gregorioscore{chants/misc.deus_in_adjutorium-T} \grechangedim{maxbaroffsettextleft}{0.6 cm}{scalable}
 \subsection{Hymnus}  \greannotation{} \index[Hymnus]{Lucis creator} \label{Lucis creator (Hymnus)} \grecommentary[0pt]{} \gresetinitiallines{1} \gresetlyriccentering{syllable} \gregorioscore{chants/hy--lucis-creator-english}
 \subsection{Antiphona}  \greannotation{VII d} \index[Antiphona]{Dixit Dominus} \label{Dixit Dominus (Antiphona)} \grecommentary[0pt]{Ps 109:1} \gresetinitiallines{1} \gresetlyriccentering{vowel} \gregorioscore{chants/an--dixit_dominus_domino_meo--dominican}
 \subsection{Psalm 109} \subsubsection{The Messiah, king and priest}  \index[Psalmus]{Psalm 109} \label{Psalm 109 (Psalmus)} \emph{Christ’s reign will last until all his enemies are made subject to him (1~Cor 15:25).}   \vspace{5pt} \par \input{chants/psalm109english3-3}
 \subsection{Antiphona}  \greannotation{T. per.} \index[Antiphona]{Ex Ægypto} \label{Ex Ægypto (Antiphona)} \grecommentary[0pt]{Cf. Ex 13:14} \gresetinitiallines{1} \gresetlyriccentering{vowel} \gregorioscore{chants/an--ex_aegypto_--solesmes--tonus-peregrinus}
 \subsection{Psalm 113A} \subsubsection{The Israelites are delivered from the bondage of Egypt}  \index[Psalmus]{Psalm 113A} \label{Psalm 113A (Psalmus)} \emph{You too left Egypt when, at baptism, you renounced that world which is at enmity with God (Saint Augustine).}   \vspace{5pt} \par \input{chants/psalm113Aenglish3-3}
 \subsection{Canticum} \subsubsection{The wedding of the Lamb}  \index[Canticum]{Salus et gloria} \label{Salus et gloria (Canticum)} \grecommentary[0pt]{Cf. Ap 19:1-2, 5-7} \gresetinitiallines{1} \gresetlyriccentering{syllable} \gregorioscore{chants/canticle--salus-et-honor--dom-1-et-3--english}
 \subsection{Lectio brevis}     \hfill \emph{2 Cor 1:3-4}   \par \lettrine[lines=3]{P}{}raised be God, the Father of our Lord Jesus Christ, the Father of mercies and the God of all consolation! He comforts us in all our afflictions and thus enables us to comfort those who are in trouble, with the same consolation we have received from him.
 \subsection{Responsorium brevis}  \greannotation{VI} \index[Responsorium brevis]{Benedictus es, Domine} \label{Benedictus es, Domine (Responsorium brevis)} \grecommentary[0pt]{Dan 3:56} \gresetinitiallines{1} \gresetlyriccentering{vowel} \gregorioscore{chants/rb--benedictus_es_domine--solesmes}

  \subsection{Antiphona ad Magnificat}  \greannotation{IV \textsc{e}} \index[Antiphona ad Magnificat]{Quid faciam} \label{Quid faciam (Antiphona ad Magnificat)} \grecommentary[0pt]{Lc 16:3-4} \gresetinitiallines{1} \gresetlyriccentering{vowel} \gregorioscore{chants/an--quid_faciam--dominican--id_6044}

 \subsection{Antiphona ad Magnificat}   \index[Antiphona ad Magnificat]{Quid faciam (text only)} \label{Quid faciam (text only) (Antiphona ad Magnificat)} \hfill \emph{Lc 16:3-4}   \begin{sloppypar} \begin{paracol}{2} \sloppy \noindent \lettrine[lines=3]{Q}{}uid fáciam, quia dóminus meus aufert a me villicatiónem? Fó\-de\-re non vá\-le\-o, men\-di\-cá\-re erubésco. Scio quid fáciam, ut cum amótus fúero a villicatióne, recípiant me in domos suas.\switchcolumn \noindent \emph{What shall I do, now that my master is taking the position of steward away from me? I am not strong enough to dig and I am ashamed to beg. I know what I shall do so that, when I am removed from the stewardship, they may welcome me into their homes.} \end{paracol} \end{sloppypar}
 \subsection{Canticum Evangelicum} \subsubsection{The soul rejoices in the Lord} \greannotation{IV \textsc{e}} \index[Canticum Evangelicum]{Magnificat 4E} \label{Magnificat 4E (Canticum Evangelicum)} \grecommentary[0pt]{Lc 1:46-55} \gresetinitiallines{1} \gresetlyriccentering{vowel} \gregorioscore{chants/magnificat4E} \input{chants/magnificat-translation}
 \subsection{Preces}   \index[Preces]{Week I, Sunday, Second Vespers} \label{Week I, Sunday, Second Vespers (Preces)}    \input{chants/intercessions-ot-sunday-week-1-2nd-vespers}
 \subsection{Pater noster}   \index[Pater noster]{Pater noster} \label{Pater noster (Pater noster)}    \gregorioscore{chants/or--pater_noster_a--solesmes-T}
 \subsection{Oratio conclusiva}        \par \lettrine[lines=3]{O}{} God, who founded all the commands of your sacred Law upon love of you and of our neighbor, grant that, by keeping your precepts, we may merit to attain eternal life. Through our Lord Jesus Christ, your Son, who lives and reigns with you in the unity of the Holy Spirit, one God, for ever and ever. \Rbar. Amen.
 \subsection{Ritus conclusionis}        \par \Vbar. The Lord be with you. \par \Rbar. And with your spirit. \par \Vbar. May almighty God bless you, the Father, and the Son, and the Holy Spirit. \par \Rbar. Amen.
 \subsection{Benedicamus Domino}   \index[Benedicamus Domino]{Sundays} \label{Sundays (Benedicamus Domino)}    \emph{Cantor:} \par \vspace{5pt} \gregorioscore{chants/misc.benedicamus.dominio.4-T}

\end{document}
