\noindent Not to us, Lord, not to us,~$\star$~

but to your name give the glory

\noindent for the sake of your love and your truth,~$\star$~

lest the heathen say: “Where is their God?”



\noindent But our God is in the heavens;~$\star$~

he does whatever he wills.

\noindent Their idols are silver and gold,~$\star$~

the work of human hands.



\noindent They have mouths but they cannot speak;~$\star$~

they have eyes but they cannot see;

\noindent they have ears but they cannot hear;~$\star$~

they have nostrils but they cannot smell.



\noindent With their hands they cannot feel;~†~

with their feet they cannot walk.~$\star$~

No sound comes from their throats.



\noindent Their makers will come to be like them~$\star$~

and so will all who trust in them.



\noindent Sons of Israel, trust in the Lord;~$\star$~

he is their help and their shield.

\noindent Sons of Aaron, trust in the Lord;~$\star$~

he is their help and their shield.



\noindent You who fear him, trust in the Lord;~$\star$~

he is their help and their shield.

\noindent He remembers us, and he will bless us;~†~

he will bless the sons of Israel.~$\star$~

He will bless the sons of Aaron.



\noindent The Lord will bless those who fear him,~$\star$~

the little no less than the great:

\noindent to you may the Lord grant increase,~$\star$~

to you and all your children.



\noindent May you be blessed by the Lord,~$\star$~

the maker of heaven and earth.

\noindent The heavens belong to the Lord~$\star$~

but the earth he has given to men.



\noindent The dead shall not praise the Lord,~$\star$~

nor those who go down into the silence.

\noindent But we who live bless the Lord~$\star$~

now and for ever. Amen.



\noindent Glory to the Father, and to the Son,~$\star$~

and to the Holy Spirit:

\noindent as it was in the beginning, is now,~$\star$~

and will be for ever. Amen.
