Not to us, Lord, not to us, *

but to your name give the glory

for the sake of your love and your truth, *

lest the heathen say: “Where is their God?”



But our God is in the heavens; *

he does whatever he wills.

Their idols are silver and gold, *

the work of human hands.



They have mouths but they cannot speak; *

they have eyes but they cannot see;

they have ears but they cannot hear; *

they have nostrils but they cannot smell.



With their hands they cannot feel; †

with their feet they cannot walk. *

No sound comes from their throats.



Their makers will come to be like them *

and so will all who trust in them.



Sons of Israel, trust in the Lord; *

he is their help and their shield.

Sons of Aaron, trust in the Lord; *

he is their help and their shield.



You who fear him, trust in the Lord; *

he is their help and their shield.

He remembers us, and he will bless us; †

he will bless the sons of Israel. *

He will bless the sons of Aaron.



The Lord will bless those who fear him, *

the little no less than the great:

to you may the Lord grant increase, *

to you and all your children.



May you be blessed by the Lord, *

the maker of heaven and earth.

The heavens belong to the Lord *

but the earth he has given to men.



The dead shall not praise the Lord, *

nor those who go down into the silence.

But we who live bless the Lord *

now and for ever. Amen.



Glory to the Father, and to the Son, *

and to the Holy Spirit:

as it was in the beginning, is now, *

and will be for ever. Amen.